Abstraction and Invariance for Algebraically Indexed Types

### 2012-07-09 paper/paper.tex
Rename the logical information flow file
Introduction, contributions
Definitions of contextual equivalence, semantic equivalence and the soundness property
Patty's changes

\documentclass[natbib,preprint]{sigplanconf}

\usepackage[usenames]{color}
\definecolor{citationcolour}{rgb}{0,0.4,0.2}
\definecolor{linkcolour}{rgb}{0,0,0.8}
\usepackage{hyperref}
\hypersetup{colorlinks=true,
            urlcolor=linkcolour,
            linkcolor=linkcolour,
            citecolor=citationcolour,
            pdftitle=Relational Parametricity for Algebraically-Indexed Types,
            pdfauthor={Robert Atkey, Neil Ghani, Patricia Johann, Andrew Kennedy},
            pdfkeywords={}}  
\def\sectionautorefname{Section}
\def\subsectionautorefname{Section}
\def\subsubsectionautorefname{Section}

@@

\newcommand{\tyInt}{\texttt{int}}
\newcommand{\tyBool}{\texttt{bool}}
\newcommand{\tyUnit}{\texttt{unit}}
\newcommand{\tyReal}{\texttt{real}}
\newcommand{\tyPrim}[2]{\textup{\texttt{#1}}\langle #2 \rangle}
\newcommand{\tyPrimNm}[1]{\texttt{#1}}
\newcommand{\primTyArity}{\mathrm{tyArity}}
\newcommand{\indexOpArity}{\mathrm{opArity}}

@@

\begin{abstract}
  Reynolds' relational parametricity provides a powerful way to reason
  about programs in terms of invariance under changes of data
  representation. A dazzling array of applications of Reynolds' theory
  exists, exploiting invariance to yield ``theorems for free'',
  uninhabitation results, and encodings of algebraic datatypes.

  Outside computer science, invariance under change is a common theme
  running through many areas mathematics and physics. For example, the
  area of a triangle is not altered by rotation or flipping. If we
  scale a triangle, then we scale its area, maintaining an invariant
  relationship between the triangle and its area. The transformations
  under which properties are invariant are often organised into
  groups, with the algebraic structure reflecting the composability
  and invertibility of transformations.

  In this paper, we investigate programming languages whose types are
  indexed by algebraic structures such as groups of geometric
  transformations. Other examples include types indexed by
  principals--for information flow security--and types indexed by
  distances--for analysis of analytic uniform continuity
  properties. Following Reynolds, we prove a general abstraction
  theorem that covers all these instances. Consequences of the
  abstraction theorem include free theorems expressing invariance
  properties of programs, type isomorphisms based on invariance
  properties, and non-definability results, indicating when certain
  algebraically indexed types are uninhabited or only inhabited by
  trivial programs.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{section-introduction.tex}
\input{geometry-twocolumn.tex}
\input{section-general-framework.tex}
\input{section-instantiations.tex}
\input{section-further-examples.tex}
\input{section-monoid.tex}
\input{section-singleton.tex}
\input{section-metric.tex}
\input{section-discussion.tex}

>>>>

\documentclass[preprint]{sigplanconf}

\usepackage[usenames]{color}
\usepackage[numbers]{natbib}
\definecolor{citationcolour}{rgb}{0,0.4,0.2}
\definecolor{linkcolour}{rgb}{0,0,0.8}
\usepackage{hyperref}
\hypersetup{colorlinks=true,
            urlcolor=linkcolour,
            linkcolor=linkcolour,
            citecolor=citationcolour,
            pdftitle=Relational Parametricity for Algebraically-Indexed Types,
            pdfauthor={Robert Atkey, Neil Ghani, Patricia Johann, Andrew Kennedy},
            pdfkeywords={}}  
\def\sectionautorefname{Section}
\def\subsectionautorefname{Section}
\def\subsubsectionautorefname{Section}

@@

\newcommand{\tyInt}{\texttt{int}}
\newcommand{\tyBool}{\texttt{bool}}
\newcommand{\tyUnit}{\texttt{unit}}
\newcommand{\tyReal}{\texttt{real}}
\newcommand{\tyPrim}[2]{\textup{\texttt{#1}}\langle #2 \rangle}
\newcommand{\tyPrimNm}[1]{\textup{\texttt{#1}}}
\newcommand{\primTyArity}{\mathrm{tyArity}}
\newcommand{\indexOpArity}{\mathrm{opArity}}

@@

\begin{abstract}
  Reynolds' relational parametricity provides a powerful way to reason
  about programs in terms of invariance under changes of data
  representation. A dazzling array of applications of Reynolds' theory
  exists, exploiting invariance to yield ``free theorems'',
  uninhabitation results, and encodings of algebraic datatypes.
  Outside computer science, invariance is a common theme running
  through many areas mathematics and physics. For example, the area of
  a triangle is unaltered by rotation or flipping. If we scale a
  triangle, then we scale its area, maintaining an invariant
  relationship between the two. The transformations under which
  properties are invariant are often organised into groups, with the
  algebraic structure reflecting the composability and invertibility
  of transformations.

  In this paper, we investigate programming languages whose types are
  indexed by algebraic structures such as groups of geometric
  transformations. Other examples include types indexed by
  principals--for information flow security--and types indexed by
  distances--for analysis of analytic uniform continuity
  properties. Following Reynolds, we prove a general abstraction
  theorem that covers all these instances. Consequences of our
  abstraction theorem include free theorems expressing invariance
  properties of programs, type isomorphisms based on invariance
  properties, and non-definability results indicating when certain
  algebraically indexed types are uninhabited or only inhabited by
  trivial programs.  Our results have been fully formalised in Coq.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{section-introduction.tex}
\input{geometry-twocolumn.tex}
\input{section-general-framework.tex}
\input{section-instantiations.tex}
\input{section-info-flow.tex}
\input{section-monoid.tex}
\input{section-singleton.tex}
\input{section-metric.tex}
\input{section-discussion.tex}
